Inferring Invariants of Distributed Programs

### 2015-05-01 Doc/evalrelate.tex
implementation

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traverse this tree and collect informations about location of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

@@

>>>>

We used Golang's \texttt{go/ast} package to parse the input program and construct the abstract syntax tree. Then we traverse this tree and collect informations about locations of \texttt{//@dump} annotations and send and receive functions. Then we added the required functions for logging the variables to the source code of the program and replaced annotations with appropriate function calls to log distributed state variables of the system.

@@

\subsubsection{Log Merger}

We used go vector clocks \cite{vclock} to keep track of vector clocks and also our merge functionality is built on top of this implementation.
